Syntax Is All You Need: A Universal-Language Approach to Mutant Generation

### 2023-03-30 paper/main.tex

\begin{table}[hbtp]
\centering
{\footnotesize % feels bad man but it's definitely easier than most other alternatives
\caption{Regex vs. Comby for Python.   LOC describes the project files considered. Muts. is total number of mutants generated for those files. \clg{FIXME: what's an invalid mutant for python?}  We can use TCE to check for redundant Python mutants, shown under ``Red.''}
\label{tab:table_python1}
\begin{tabularx}{\columnwidth}{l|r|rcr|rcr}
\toprule\toprule
                 &                 & \multicolumn{3}{c|}{\textbf{Regex}}             &\multicolumn{3}{c}{\textbf{Comby}}  \\[1ex]
\textbf{Project} & \textbf{LOC}    & \textbf{Muts.} & \textbf{Red.}  & \textbf{\% Valid} & \textbf{Muts.} & \textbf{Red.}   &  \textbf{\% Valid} \\\midrule
keract           & 402             & 3984  & 729   & 41.53\%           & 3067  & 533    & 47.96\% \\
dtw              & 118             & 2106  & 567   & 46.20\%           & 1835  & 639    & 47.19\% \\
notion-          & \mr{2}{189}     & \mr{2}{1038}  & \mr{2}{82}    & \mr{2}{18.89\%}           & \mr{2}{1019}  & \mr{2}{122}    & \mr{2}{19.23\%} \\
sdk-py           & & & & & & \\[0.5ex]
atlassian-       & \mr{2}{236}      & \mr{2}{1511}  & \mr{2}{207}   & \mr{2}{19.99\%}           & 1319  & \mr{2}{351}    & \mr{2}{25.25\%} \\
python-api       & & & & & & \\[0.5ex]
ESD              & 698             & 6268  & 1642  & 29.46\%           & 3874  & 614    & 44.18\% \\
fiber            & 358             & 1565  & 163   & 31.08\%           & 1466  & 241    & 31.24\% \\\bottomrule
\end{tabularx}
\begin{tabularx}{\columnwidth}{Xllrrrrrr}
                  && &  \textbf{Red.}     & \textbf{Valid}  & \textbf{Invalid}  & \textbf{\% Valid} \\\midrule
\multirow{4}{*}{\textbf{Overall}} & \multirow{2}{*}{Regex} & Mean &  565.00 & 913.00 & 1267.33 & 31.19\%  & \\
    &   &  Std.Dev. & 584.79  & 708.93 & 813.35 & 11.06\%  \\
 & \multirow{2}{*}{Comby} & Mean & 416.67 & 839.33 & 840.67 & 35.84\% \\
  &   &  Std.Dev. &  211.62 & 628.79 & 418.99 & 12.28\%   \\\bottomrule
\end{tabularx}}
\end{table}

>>>>

\begin{table}[hbtp]
\centering
{\footnotesize % feels bad man but it's definitely easier than most other alternatives
\caption{Regex vs. Comby for Python.   LOC describes the project files
  considered. Muts. is total number of mutants generated for those
  files.  Invalid mutants are ones that fail module load (e.g., due
  to imbalanced parenthesis, bad indentation, or similar problems).  We can use TCE to check for redundant Python mutants, shown under ``Red.''}
\label{tab:table_python1}
\begin{tabularx}{\columnwidth}{l|r|rcr|rcr}
\toprule\toprule
                 &                 & \multicolumn{3}{c|}{\textbf{Regex}}             &\multicolumn{3}{c}{\textbf{Comby}}  \\[1ex]
\textbf{Project} & \textbf{LOC}    & \textbf{Muts.} & \textbf{Red.}  & \textbf{\% Valid} & \textbf{Muts.} & \textbf{Red.}   &  \textbf{\% Valid} \\\midrule
keract           & 402             & 3984  & 729   & 41.53\%           & 3067  & 533    & 47.96\% \\
dtw              & 118             & 2106  & 567   & 46.20\%           & 1835  & 639    & 47.19\% \\
notion-          & \mr{2}{189}     & \mr{2}{1038}  & \mr{2}{82}    & \mr{2}{18.89\%}           & \mr{2}{1019}  & \mr{2}{122}    & \mr{2}{19.23\%} \\
sdk-py           & & & & & & \\[0.5ex]
atlassian-       & \mr{2}{236}      & \mr{2}{1511}  & \mr{2}{207}   & \mr{2}{19.99\%}           & 1319  & \mr{2}{351}    & \mr{2}{25.25\%} \\
python-api       & & & & & & \\[0.5ex]
ESD              & 698             & 6268  & 1642  & 29.46\%           & 3874  & 614    & 44.18\% \\
fiber            & 358             & 1565  & 163   & 31.08\%           & 1466  & 241    & 31.24\% \\\bottomrule
\end{tabularx}
\begin{tabularx}{\columnwidth}{Xllrrrrrr}
                  && &  \textbf{Red.}     & \textbf{Valid}  & \textbf{Invalid}  & \textbf{\% Valid} \\\midrule
\multirow{4}{*}{\textbf{Overall}} & \multirow{2}{*}{Regex} & Mean &  565.00 & 913.00 & 1267.33 & 31.19\%  & \\
    &   &  Std.Dev. & 584.79  & 708.93 & 813.35 & 11.06\%  \\
 & \multirow{2}{*}{Comby} & Mean & 416.67 & 839.33 & 840.67 & 35.84\% \\
  &   &  Std.Dev. &  211.62 & 628.79 & 418.99 & 12.28\%   \\\bottomrule
\end{tabularx}}
\end{table}
